Rust for Scientific Computing

### 2025-09-13 paper/main.tex
insert table later

\begin{figure*}
    \centering
    \includegraphics[width=0.5\textwidth]{figures/stackoverflow-popular-languages.pdf}%
    \includegraphics[width=0.5\textwidth]{figures/pypi-org-used-languages.pdf}
    \caption{
        Usage of programming languages according to (A) stackoverflow.com and (B) pypi.org.
    }
\end{figure*}
\begin{figure*}
    \centering
    \includegraphics[width=0.5\textwidth]{figures/stackoverflow-loved-language.pdf}%
    \includegraphics[width=0.5\textwidth]{figures/stackoverflow-desired-language.pdf}
    \caption{
        Popularity of the Rust programming language.
    }
\end{figure*}
\begin{figure*}
    \centering
    \includegraphics[width=0.5\textwidth]{figures/crates-io-release-numbers.pdf}
    \caption{
        Number of releases of all included crates.
        Measure of overall growth of the field.
    }
\end{figure*}

>>>>

\begin{figure*}
    \centering
    \includegraphics[width=0.5\textwidth]{figures/stackoverflow-popular-languages.pdf}%
    \includegraphics[width=0.5\textwidth]{figures/pypi-org-used-languages.pdf}
    \caption{
        Usage of programming languages according to (A) stackoverflow.com and (B) pypi.org.
    }
\end{figure*}
\begin{figure*}
    \centering
    \includegraphics[width=0.5\textwidth]{figures/stackoverflow-loved-language.pdf}%
    \includegraphics[width=0.5\textwidth]{figures/stackoverflow-desired-language.pdf}
    \caption{
        Popularity of the Rust programming language.
    }
\end{figure*}
\begin{figure*}
    \centering
    \includegraphics[width=0.5\textwidth]{figures/crates-io-release-numbers.pdf}%
    \includegraphics[width=0.5\textwidth]{figures/crates-io-deps-downloads-scatter.pdf}
    \caption{
        Number of releases of all included crates.
        Measure of overall growth of the field.
        The second figure can be misleading since this will for example not capture the setup where
        a crate is the dependency of a pypi.org package which is downloaded very often.
        The colors and size of the markers are also scaled logarithmically with the number of total
        downloads.
    }
\end{figure*}
